---
title: "R Shiny Intro Pres"
author: "John Muschelli"
date: '`r Sys.Date()`'
output: 
  ioslides_presentation:
    logo: logo.png
    incremental: true
runtime: shiny
---

## Shiny in R

- What is Shiny in R?

> - A web application framework for R
> - Turn your analyses into interactive web applications

- No HTML, CSS, or JavaScript knowledge required*
- (*Sort of)
- Go to the [Gallery](http://shiny.rstudio.com/gallery/)


## Default Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```


## Why Shiny?

- Let's just step back and talk about what this slide deck is 
- The user can INTERACT with the data and R
- Usually, only one of them is possible
- No Code - complete web app
> - Can use all the things R has to offer
> - Look at all these [Widgets!](http://shiny.rstudio.com/gallery/widget-gallery.html)


## Shiny Code ecample


```{r, echo=FALSE}
library(shinyAce)
  inputPanel(
    div(
      class = "form-group shiny-input-container", 
      style = paste0("width: ", validateCssUnit("100%"), ";"), 
      tags$label("R code to run", `for` = "r_code"),
      tags$input(id = "r_code", type = "text", 
class = "form-control", 
value = 'hist(faithful$eruptions, 
      probability = TRUE, 
        breaks = 20,
       xlab = "Duration (minutes)", 
       main = "Geyser eruption duration")'))
)
    
    #   textInput("r_code", label = "R code to run",
    #             value = 'hist(faithful$eruptions, 
    #       probability = TRUE, 
    #         breaks = 20,
    #        xlab = "Duration (minutes)", 
    #        main = "Geyser eruption duration")', width = "100%")
  # ),
  renderPlot({
    eval(parse(text = input$r_code))
  })
# )
```




## Default Interactive Plot Input (UI) Code

```{r, echo=TRUE, eval = FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)
```


## Default Interactive Plot Output (Server) Code

```{r, echo=TRUE, eval = FALSE}
renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```



## Just quick table (ugly)

```{r}
summary(cars)
```

## Just quick table (less ugly, but still ugly)

```{r}
renderTable({
  summary(cars)
})
```

## Just quick table (less ugly, but still ugly)

Takes same arguments as `print.xtable`
```{r}
renderTable({
  summary(cars)
}, include.rownames = FALSE)
```



## DataTables in Shiny

```{r, echo = FALSE}
renderDataTable({
  cars
})
```

## DataTables in Shiny

```{r, echo = TRUE, eval = FALSE}
renderDataTable({
  cars
})
```

