---
title: "R Shiny Intro Pres"
author: "John Muschelli"
date: '`r Sys.Date()`'
output: 
  ioslides_presentation:
    logo: logo.png
    incremental: true
runtime: shiny
---

## Shiny in R

- What is Shiny in R?

> - A web application framework for R
> - Turn your analyses into interactive web applications

- No HTML, CSS, or JavaScript knowledge required*
- (*Sort of)
- Go to the [Gallery](http://shiny.rstudio.com/gallery/)


## Default Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```


## Why Shiny?

- The user can INTERACT with the data and R
- Usually, only one of them is possible
- No Code - complete web app
- Can use all the things R has to offer


## Default Interactive Plot Input (UI) Code

```{r, echo=TRUE, eval = FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)
```


## Default Interactive Plot Output (Server) Code

```{r, echo=TRUE, eval = FALSE}
renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```



## Just quick table (ugly)

```{r}
summary(cars)
```

## Just quick table (less ugly, but still ugly)

```{r}
renderTable({
  summary(cars)
})
```

## Just quick table (less ugly, but still ugly)

Takes same arguments as `print.xtable`
```{r}
renderTable({
  summary(cars)
}, include.rownames = FALSE)
```



## DataTables in Shiny

```{r, echo = FALSE}
renderDataTable({
  cars
  })
```

## DataTables in Shiny

```{r, echo = TRUE, eval = FALSE}
renderDataTable({
  cars
  })
```


